Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-02-14 3dpas_intro.tex
checkpoint.
updated abstract

\begin{abstract}
  A common feature across many science and engineering applications is the
  amount and diversity of data and computation that must be integrated to yield
  insights. Often data is increasingly large-scale and distributed; their
  location, availability and properties are time-dependent. Collectively these
  give rise to dynamic distributed data intensive applications. ``Static'' data
  have received significant attention.  The characteristics, requirements, and
  software systems for the analysis of large volumes of dynamic, distributed and
  data intensive have however received relatively less. This paper surveys
  several representative dynamic distributed data-intensive application
  scenarios, provides a common conceptual framework to understand them as well
  as examines the infrastructure used in support of applications.

>>>>

\begin{abstract}
  A common feature across many science and engineering applications is the
  amount and diversity of data and computation that must be integrated to yield
  insights. Often data are increasingly large-scale and distributed; and their
  location, availability and properties are time-dependent. Collectively, these
  characteristics give rise to dynamic distributed data intensive applications. While ``static'' data
  application have received significant attention, the characteristics, requirements, and
  software systems for the analysis of large volumes of dynamic, distributed, and
  data intensive have received relatively less. This paper surveys
  several representative dynamic distributed data-intensive application
  scenarios, provides a common conceptual framework to understand them, and
  examines the infrastructure used in support of applications.
